Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
fixing reference mistake.

    \end{tikzpicture}
    \caption{The pattern graph $P$ on the left cannot be found in the target graph $T$, but if
    the central vertex in $P$ is removed, then a subgraph isomorphism exists.}
    \label{fig:subgraphexample}
\end{figure}

@@

In this work we discuss an intermediate problem, where we must map all but $k$ vertices of the
pattern graph into the target---we show an example in \cref{fig:subgraphexample}. This in some
ways resembles the approximate subgraph matching model of \citet{DBLP:conf/cp/ZampelliDD05},
although we allow any vertex to be removed. We show that if
$k$ is reasonably small (say, between 1 and 5), then weakened forms of degree and path based
filterings are still effective in pruning the initial search space and in providing additional
constraints respectively. We then show that combining these techniques leads to a practical
algorithm which can scale to work with the families of graphs commonly used to benchmark subgraph
isomorphism algorithms: depending upon the benchmark family, we can close a substantial portion of
the instances, and in many more cases, we can at least obtain an upper bound. This is a significant
improvement over state of the art maximum common subgraph solvers, which cannot even fit many of
these instances in RAM. Finally, we show that iteratively increasing $k$ gives a competitive
algorithm for the maximum common induced subgraph problem.

@@

>>>>

    \end{tikzpicture}
    \caption{The pattern graph $P$ on the left cannot be found in the target graph $T$, but if
    the central vertex in $P$ is removed, then a subgraph isomorphism exists.}
    \label{figure:subgraphexample}
\end{figure}

@@

In this work we discuss an intermediate problem, where we must map all but $k$ vertices of the
pattern graph into the target---we show an example in \cref{figure:subgraphexample}. This in some
ways resembles the approximate subgraph matching model of \citet{DBLP:conf/cp/ZampelliDD05},
although we allow any vertex to be removed. We show that if
$k$ is reasonably small (say, between 1 and 5), then weakened forms of degree and path based
filterings are still effective in pruning the initial search space and in providing additional
constraints respectively. We then show that combining these techniques leads to a practical
algorithm which can scale to work with the families of graphs commonly used to benchmark subgraph
isomorphism algorithms: depending upon the benchmark family, we can close a substantial portion of
the instances, and in many more cases, we can at least obtain an upper bound. This is a significant
improvement over state of the art maximum common subgraph solvers, which cannot even fit many of
these instances in RAM. Finally, we show that iteratively increasing $k$ gives a competitive
algorithm for the maximum common induced subgraph problem.

@@

% Other stuff to stick back in: proofs, example of paths of length 3, correlation heatmap
